---
title: "Biofilm Community Comparison across the Classification Levels"
output: html_notebook
---

# Set working directory
```{r}
setwd("G:/FIWI/06_Shared folders/Jessica_Irene_PhD/01_Microbial in Aquaculture/Manuscript/Additional Information")
getwd()
```

# Load libraries
```{r}
library(dplyr)
library(tidyverse)
library(readxl)
```


################# EARTH PRIMERS #######################

# Load data
```{r}
earth.farmA.biofilm <- read_excel("G:/FIWI/06_Shared folders/Jessica_Irene_PhD/01_Microbial in Aquaculture/Manuscript/Additional Information/additional file_4_biofilm.xlsx", sheet="Earth_FarmA_Biofilm.rps")
```

### EARTH BIOFILM FARM A ###

# ASV and read count for Earth Biofilm Farm A - Kingdom
```{r}
e.kingdom.farmA <- earth.farmA.biofilm %>%
  group_by(Kingdom) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.kingdom.farmA

write.csv(e.kingdom.farmA, "e.kingdom.farmA_biofilm.csv")
```

# ASV and read count for Earth Biofilm Farm A - Phylum
```{r}
e.phylum.farmA <- earth.farmA.biofilm %>%
  group_by(Phylum) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.phylum.farmA

write.csv(e.phylum.farmA, "e.phylum.farmA_biofilm.csv")
```

# ASV and read count for Earth Biofilm Farm A - Class
```{r}
e.class.farmA <- earth.farmA.biofilm %>%
  group_by(Class) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.class.farmA

write.csv(e.class.farmA, "e.class.farmA_biofilm.csv")
```

# ASV and read count for Earth Biofilm Farm A - Order
```{r}
e.order.farmA <- earth.farmA.biofilm %>%
  group_by(Order) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.order.farmA

write.csv(e.order.farmA, "e.order.farmA_biofilm.csv")
```

# ASV and read count for Earth Biofilm Farm A - Family
```{r}
e.family.farmA <- earth.farmA.biofilm %>%
  group_by(Family) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.family.farmA

write.csv(e.family.farmA, "e.family.farmA_biofilm.csv")
```

# ASV and read count for Earth Biofilm Farm A - Genus
```{r}
e.genus.farmA <- earth.farmA.biofilm %>%
  group_by(Genus) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.genus.farmA 

write.csv(e.genus.farmA , "e.genus.farmA_biofilm.csv")
```



###### EARTH FARM B BIOFILM ###### 

# Load data
```{r}
earth.farmB.biofilm <- read_excel("G:/FIWI/06_Shared folders/Jessica_Irene_PhD/01_Microbial in Aquaculture/Manuscript/Additional Information/additional file_4_biofilm.xlsx", sheet="Earth_FarmB_Biofilm.rps")
```


# ASV and read count for Earth Biofilm Farm B - Kingdom
```{r}
e.kingdom.farmB <- earth.farmB.biofilm %>%
  group_by(Kingdom) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.kingdom.farmB

write.csv(e.kingdom.farmB, "e.kingdom.farmB_biofilm.csv")
```

# ASV and read count for Earth Biofilm Farm B - Phylum
```{r}
e.phylum.farmB <- earth.farmB.biofilm %>%
  group_by(Phylum) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.phylum.farmB

write.csv(e.phylum.farmB, "e.phylum.farmB_biofilm.csv")
```

# ASV and read count for Earth Biofilm Farm B - Class
```{r}
e.class.farmB <- earth.farmB.biofilm %>%
  group_by(Class) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.class.farmB

write.csv(e.class.farmB, "e.class.farmB_biofilm.csv")
```

# ASV and read count for Earth Biofilm Farm B - Order
```{r}
e.order.farmB <- earth.farmB.biofilm %>%
  group_by(Order) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.order.farmB

write.csv(e.order.farmB, "e.order.farmB_biofilm.csv")
```

# ASV and read count for Earth Biofilm Farm B - Family
```{r}
e.family.farmB <- earth.farmB.biofilm %>%
  group_by(Family) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.family.farmB

write.csv(e.family.farmB, "e.family.farmB_biofilm.csv")
```

# ASV and read count for Earth Biofilm Farm B - Genus
```{r}
e.genus.farmB <- earth.farmB.biofilm %>%
  group_by(Genus) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.genus.farmB 

write.csv(e.genus.farmB , "e.genus.farmB_biofilm.csv")
```



####### MISEQ FARM A  #########

# Load data
```{r}
miseq.farmA.biofilm <- read_excel("G:/FIWI/06_Shared folders/Jessica_Irene_PhD/01_Microbial in Aquaculture/Manuscript/Additional Information/additional file_4_biofilm.xlsx", sheet="MiSeq_FarmA_Biofilm.rps")
```

### MISEQ BIOFILM FARM A ###

# ASV and read count for MiSeq Biofilm Farm A - Kingdom
```{r}
m.kingdom.farmA <- miseq.farmA.biofilm %>%
  group_by(Kingdom) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.kingdom.farmA

write.csv(m.kingdom.farmA, "m.kingdom.farmA_biofilm.csv")
```

# ASV and read count for MiSeq Biofilm Farm A - Phylum
```{r}
m.phylum.farmA <- miseq.farmA.biofilm %>%
  group_by(Phylum) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.phylum.farmA

write.csv(m.phylum.farmA, "m.phylum.farmA_biofilm.csv")
```

# ASV and read count for MiSeq Biofilm Farm A - Class
```{r}
m.class.farmA <- miseq.farmA.biofilm %>%
  group_by(Class) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.class.farmA

write.csv(m.class.farmA, "m.class.farmA_biofilm.csv")
```

# ASV and read count for MiSeq Biofilm Farm A - Order
```{r}
m.order.farmA <- miseq.farmA.biofilm %>%
  group_by(Order) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.order.farmA

write.csv(m.order.farmA, "m.order.farmA_biofilm.csv")
```

# ASV and read count for Earth Biofilm Farm A - Family
```{r}
m.family.farmA <- miseq.farmA.biofilm %>%
  group_by(Family) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.family.farmA

write.csv(m.family.farmA, "m.family.farmA_biofilm.csv")
```

# ASV and read count for MiSeq Biofilm Farm A - Genus
```{r}
m.genus.farmA <- miseq.farmA.biofilm %>%
  group_by(Genus) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.genus.farmA 

write.csv(m.genus.farmA , "m.genus.farmA_biofilm.csv")
```



###### MISEQ FARM B BIOFILM ###### 

# Load data
```{r}
miseq.farmB.biofilm <- read_excel("G:/FIWI/06_Shared folders/Jessica_Irene_PhD/01_Microbial in Aquaculture/Manuscript/Additional Information/additional file_4_biofilm.xlsx", sheet="MiSeq_FarmB_Biofilm.rps")
```

### MISEQ BIOFILM FARM B ###

# ASV and read count for MiSeq Biofilm Farm B - Kingdom
```{r}
m.kingdom.farmB <- miseq.farmB.biofilm %>%
  group_by(Kingdom) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.kingdom.farmB

write.csv(m.kingdom.farmB, "m.kingdom.farmB_biofilm.csv")
```

# ASV and read count for MiSeq Biofilm Farm B - Phylum
```{r}
m.phylum.farmB <- miseq.farmB.biofilm %>%
  group_by(Phylum) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.phylum.farmB

write.csv(m.phylum.farmB, "m.phylum.farmB_biofilm.csv")
```

# ASV and read count for MiSeq Biofilm Farm B - Class
```{r}
m.class.farmB <- miseq.farmB.biofilm %>%
  group_by(Class) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.class.farmB

write.csv(m.class.farmB, "m.class.farmB_biofilm.csv")
```

# ASV and read count for MiSeq Biofilm Farm B - Order
```{r}
m.order.farmB <- miseq.farmB.biofilm %>%
  group_by(Order) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.order.farmB

write.csv(m.order.farmB, "m.order.farmB_biofilm.csv")
```

# ASV and read count for Earth Biofilm Farm B - Family
```{r}
m.family.farmB <- miseq.farmB.biofilm %>%
  group_by(Family) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.family.farmB

write.csv(m.family.farmB, "m.family.farmB_biofilm.csv")
```

# ASV and read count for MiSeq Biofilm Farm B - Genus
```{r}
m.genus.farmB <- miseq.farmB.biofilm %>%
  group_by(Genus) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.genus.farmB

write.csv(m.genus.farmB , "m.genus.farmB_biofilm.csv")
```


####### EARTH YOUNG BIOFILM FARM A ###########

# Load data
```{r}
earth.young <- read_excel("G:/FIWI/06_Shared folders/Jessica_Irene_PhD/01_Microbial in Aquaculture/Manuscript/Additional Information/additional file_4_biofilm.xlsx", sheet="Earth_YoungBiofilm.rps")
```

# ASV and read count for Earth Young Biofilm - Kingdom
```{r}
e.kingdom.y <- earth.young %>%
  group_by(Kingdom) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.kingdom.y


write.csv(e.kingdom.y, "e.kingdom_youngbiofilm.csv")
```

# ASV and read count for Earth Young Biofilm - Phylum
```{r}
e.phylum.y <- earth.young %>%
  group_by(Phylum) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.phylum.y

write.csv(e.phylum.y, "e.phylum_youngbiofilm.csv")
```

# ASV and read count for Earth Young Biofilm - Class
```{r}
e.class.y <- earth.young %>%
  group_by(Class) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.class.y

write.csv(e.class.y, "e.class_youngbiofilm.csv")
```

# ASV and read count for Earth Young Biofilm - Order
```{r}
e.order.y <- earth.young %>%
  group_by(Order) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.order.y

write.csv(e.order.y, "e.order_youngbiofilm.csv")
```

# ASV and read count for Earth Young Biofilm - Family
```{r}
e.family.y <- earth.young %>%
  group_by(Family) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.family.y

write.csv(e.family.y, "e.family_youngbiofilm.csv")
```

# ASV and read count for Earth Young Biofilm - Genus
```{r}
e.genus.y <- earth.young %>%
  group_by(Genus) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.genus.y

write.csv(e.genus.y, "e.genus_youngbiofilm.csv")
```




##### EARTH MATURE BIOFILM #####

# Load data
```{r}
earth.mature <- read_excel("G:/FIWI/06_Shared folders/Jessica_Irene_PhD/01_Microbial in Aquaculture/Manuscript/Additional Information/additional file_4_biofilm.xlsx", sheet="Earth_MatureBiofilm.rps")
```


# ASV and read count for Earth Mature Biofilm - Kingdom
```{r}
e.kingdom.m <- earth.mature %>%
  group_by(Kingdom) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.kingdom.m


write.csv(e.kingdom.m, "e.kingdom_maturebiofilm.csv")
```

# ASV and read count for Earth Mature Biofilm - Phylum
```{r}
e.phylum.m <- earth.mature %>%
  group_by(Phylum) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.phylum.m

write.csv(e.phylum.m, "e.phylum_maturebiofilm.csv")
```

# ASV and read count for Earth Mature Biofilm - Class
```{r}
e.class.m <- earth.mature %>%
  group_by(Class) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.class.m

write.csv(e.class.m, "e.class_maturebiofilm.csv")
```

# ASV and read count for Earth Mature Biofilm - Order
```{r}
e.order.m <- earth.mature %>%
  group_by(Order) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.order.m

write.csv(e.order.m, "e.order_maturebiofilm.csv")
```

# ASV and read count for Earth Mature Biofilm - Family
```{r}
e.family.m <- earth.mature %>%
  group_by(Family) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.family.m

write.csv(e.family.m, "e.family_maturebiofilm.csv")
```

# ASV and read count for Earth Mature Biofilm - Genus
```{r}
e.genus.m <- earth.mature %>%
  group_by(Genus) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

e.genus.m

write.csv(e.genus.m, "e.genus_maturebiofilm.csv")
```


####################  MISEQ PRIMERS ##############################



### MISEQ YOUNG BIOFILM ###

# Load data
```{r}
miseq.young <- read_excel("G:/FIWI/06_Shared folders/Jessica_Irene_PhD/01_Microbial in Aquaculture/Manuscript/Additional Information/additional file_4_biofilm.xlsx", sheet="MiSeq_YoungBiofilm.rps")
```


# ASV and read count for Miseq Young Biofilm - Kingdom
```{r}
m.kingdom.y <- miseq.young %>%
  group_by(Kingdom) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.kingdom.y


write.csv(m.kingdom.y, "m.kingdom_youngbiofilm.csv")
```

# ASV and read count for Miseq Young Biofilm - Phylum
```{r}
m.phylum.y <- miseq.young %>%
  group_by(Phylum) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.phylum.y

write.csv(m.phylum.y, "m.phylum_youngbiofilm.csv")
```

# ASV and read count for Miseq Young Biofilm - Class
```{r}
m.class.y <- miseq.young %>%
  group_by(Class) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.class.y

write.csv(m.class.y, "m.class_youngbiofilm.csv")
```

# ASV and read count for Miseq Young Biofilm - Order
```{r}
m.order.y <- miseq.young %>%
  group_by(Order) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.order.y

write.csv(m.order.y, "m.order_youngbiofilm.csv")
```

# ASV and read count for Miseq Young Biofilm - Family
```{r}
m.family.y <- miseq.young %>%
  group_by(Family) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.family.y

write.csv(m.family.y, "m.family_youngbiofilm.csv")
```

# ASV and read count for Miseq Young Biofilm - Genus
```{r}
m.genus.y <- miseq.young %>%
  group_by(Genus) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.genus.y

write.csv(m.genus.y, "m.genus_youngbiofilm.csv")
```




##### MISEQ MATURE BIOFILM #####

# Load data
```{r}
miseq.mature <- read_excel("G:/FIWI/06_Shared folders/Jessica_Irene_PhD/01_Microbial in Aquaculture/Manuscript/Additional Information/additional file_4_biofilm.xlsx", sheet="MiSeq_MatureBiofilm.rps")
```

# ASV and read count for Miseq Mature Biofilm - Kingdom
```{r}
m.kingdom.m <- miseq.mature %>%
  group_by(Kingdom) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.kingdom.m


write.csv(m.kingdom.m, "m.kingdom_maturebiofilm.csv")
```

# ASV and read count for Miseq Mature Biofilm - Phylum
```{r}
m.phylum.m <- miseq.mature %>%
  group_by(Phylum) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.phylum.m

write.csv(m.phylum.m, "m.phylum_maturebiofilm.csv")
```

# ASV and read count for Miseq Mature Biofilm - Class
```{r}
m.class.m <- miseq.mature %>%
  group_by(Class) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.class.m

write.csv(m.class.m, "m.class_maturebiofilm.csv")
```

# ASV and read count for Miseq Mature Biofilm - Order
```{r}
m.order.m <- miseq.mature %>%
  group_by(Order) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.order.m

write.csv(m.order.m, "m.order_maturebiofilm.csv")
```

# ASV and read count for Miseq Mature Biofilm - Family
```{r}
m.family.m <- miseq.mature %>%
  group_by(Family) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.family.m

write.csv(m.family.m, "m.family_maturebiofilm.csv")
```

# ASV and read count for Miseq Mature Biofilm - Genus
```{r}
m.genus.m <- miseq.mature %>%
  group_by(Genus) %>%
  summarize(count_asvs = n(), sum_reads = sum(Reads))

m.genus.m

write.csv(m.genus.m, "m.genus_maturebiofilm.csv")
```


